The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-19 dit-paper_ieee.tex
New NoFPDIT graph
Close #28 and reworded task generation and fig description for noFPDIT simulation

		The values of the $n_i$ are given by \cite{baruah1999generalized}
		\begin{equation}
			n_i(t_1, t_2) =
			\left\llbracket
				\left\lfloor
					\frac{t_2 - O_i - D_i}{T_i}
				\right\rfloor -
				\left\lceil
					\frac{t_1 - O_i}{T_i}
				\right\rceil + 1
			\right\rrbracket_0
		\end{equation}
		where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.

@@

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3, 4 and 5.
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figs/nofpdit_3.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

	We observe that when the CDF tends to zero, few systems have a FPDIT.
	This is easily explained by the fact that
	a high CDF means more idle instants for each task, and thus more opportunities
	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
	happen, a higher number of tasks results in a decrease in FPDIT density.

>>>>

		The values of the $n_i$ are given by \cite{baruah1990algorithms}
		\begin{equation}
			n_i(t_1, t_2) =
			\left\llbracket
				\left\lfloor
					\frac{t_2 - O_i - D_i}{T_i}
				\right\rfloor -
				\left\lceil
					\frac{t_1 - O_i}{T_i}
				\right\rceil + 1
			\right\rrbracket_0
		\end{equation}
		where $\llbracket x \rrbracket_0$ stands for $\max \{ 0, x \}$.

@@

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}

@@

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{figs/nofpdit_4.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

	We observe that when the CDF is close to zero, fewer systems have a FPDIT.
	This is easily explained by the fact that
	a high CDF means more idle instants for each task, and thus more opportunities
	for DITs to happen. Similarly, as all tasks must be synchronized for a DIT to
	happen, a higher number of tasks results in a decrease in FPDIT density.
